### 2015-02-18 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report to include TN number, update input file for high frame rate slices

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2015) \\
CODEN: NTNOEF}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup
\vfill

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1870}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1870}{http://dx.doi.org/10.6028/NIST.TN.1870}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1870}{http://dx.doi.org/10.6028/NIST.TN.1870} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1870 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1870, \pageref{LastPage} pages (February 2015) \\
CODEN: NTNOEF}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1870}{\bf http://dx.doi.org/10.6028/NIST.TN.1870} \\
\endgroup
\vfill
